Ceph Parallel File System Evaluation Report

### 2013-08-27 testbed.tex
minor changes to section 2

Our testing methodology is bottom to top. We start our evaluation from the
lowest level (i.e. block-level) and work our way up to the top (i.e. file
system-level). We establish an expected theoretical performance of a given
hardware or software layer and then compare that with the observed results of
our experiments. Each added new layer to the stack introduces new bottlenecks
and re-defines the expected theoretical performance of the overall system. We
will explain each component or layer and its expected performance before we
present our observed results.

Our tools for benchmarking and evaluating different layers also change as we go
up the stack.  For example, a tool perfect for assessing block-level
performance over a single server host might be completely inadequate for
observing parallel file system performance over multiple clients. As we present
our evaluations, we will also introduce and explain our benchmark tools, in
this paper.

>>>>

Our testing methodology is bottom to top. We start our evaluation from the
lowest level (i.e. block-level)  to establish a baseline performance and work
our way up to the top (i.e. file system-level). We establish an expected
theoretical performance of a given hardware or software layer and then compare
that with the observed results of our experiments. Each added new layer to the
stack introduces new bottlenecks and re-defines the expected theoretical
performance of the overall system. We will explain each component or layer and
its expected performance before we present our observed results.

Our tools for benchmarking and evaluating different layers also change as we go
up in the stack.  For example, a tool perfect for assessing block-level
performance over a single server host might be completely inadequate for
observing parallel file system performance over multiple clients. As we present
our evaluations, we will also introduce and explain our benchmark tools, in
this paper.
